GHRVis:

### 2022-02-23 paper/section/main.tex
draft: update algorithm

    \textbf{Global variables:} \\
    $ \mathcal{C}_l \gets $ the length of a corridor \\
    $ \mathcal{C}_w \gets $ the width of a corridor \\
    $ \mathcal{D} \gets $ the distance to move nodes within the corridor \\
    $ \mathcal{S} \gets $ the current size of all nodes \\

@@

            \ForEach{$ {n}_{in}^i $ inside $ corridor $}
                \State $ e_{d} = $ \Call{DeriveEdge}{$ slope $, $ {n}_{in}^i $, $ \mathcal{D} $}

@@

        \Switch{$Slope$}
            \Case{$0$}
                \If{$ IsSideEdge = True $}
                    \State $ a.x \gets Point.x $
                \Else
                    \State $ a.x \gets Point.x + Length $
                \EndIf
                \State $ a.y \gets Point.y $
                \State $ b.x \gets Point.x - Length $,~$ b.y \gets Point.y $
            \EndCase
            \Case{$ \infty $ or $ -\infty $}
                \State $ a.x \gets Point.x $

@@

@@

                \State $ b.x \gets Point.x - \Delta x $,~$ b.y \gets Point.y - \Delta y $
            \EndDefault

>>>>

    \textbf{Global variables:} \\
    $ \mathcal{C}_l \gets $ the length of a corridor \\
    $ \mathcal{C}_w \gets $ the width of a corridor \\
    $ \mathcal{D} \gets $ the distance to move nodes within the corridor \\

@@

            \ForEach{$ {n}_{in}^i $ inside $ corridor $}
                \State $ {n}_{in}^i.dx \gets \Delta x $, $ {n}_{in}^i.dy \gets \Delta y $
                \State $ e_{d} = $ \Call{DeriveEdge}{$ slope $, $ {n}_{in}^i $, $ \mathcal{D} $}

@@

        \Switch{$Slope$}
            \Case{$0$}
                \If{$ IsSideEdge = True $}
                    \State $ a.x \gets Point.x $
                \Else
                    \State $ a.x \gets Point.x + Length $
                \EndIf
                \State $ a.y \gets Point.y $

                \If{$ Point.dx < 0 $}
                    \State $ a.x \gets Point.x + Length $
                \Else
                    \State $ a.x \gets Point.x - Length $
                \EndIf
                \State $ b.x \gets Point.x - Length $,~$ b.y \gets Point.y $
            \EndCase
            \Case{$ \infty $ or $ -\infty $}
                \State $ a.x \gets Point.x $

@@

                \If{$ Point.dy < 0 $}
                    \State $ a.y \gets Point.y + Length $
                \Else
                    \State $ a.y \gets Point.y - Length $
                \EndIf

@@

                \If{$ Point.dx > 0 $ and $ Slope = 1 $ and $ IsSideEdge = True $}
                    \State $ b.x \gets Point.x + \Delta x $,~$ b.y \gets Point.y + \Delta y $
                \Else
                    \State $ b.x \gets Point.x - \Delta x $,~$ b.y \gets Point.y - \Delta y $
                \EndIf

            \EndDefault
